% The Quantum Internet - A New Frontier
% Peter P. Rohde et al.

% Publication mode:
%   0 = Draft (figures disabled, quicker compiling)
%   1 = Preprint (for Red Pen of Death - Dowling's eyes only)
%   2 = Two-column article
%   3 = Single-column book

% Sketches mode:
%	0 = off
%	1 = on

% Set numbers here

\def\pubmode{2}
\def\sketchesmode{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%

\if 0\pubmode % Draft mode (figures disabled)
	\documentclass[draft, twocolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-1}
	\let\stdsection\section
	\renewcommand\section{\newpage\stdsection}
\fi

\if 1\pubmode % Preprint (Dowling's eyes only)
	\documentclass[preprint, aps, rmp, singlecolumn, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-1}
\fi

\if 2\pubmode % Two-column article
	\documentclass[twocolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-1}
\fi

\if 3\pubmode % Single-column book
	\documentclass[singlecolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-1}
	\let\stdpart\part
	\renewcommand\part{\newpage\stdpart}
\fi

\input{Sections/packages}

\input{Sections/commands_and_definitions}

\hypersetup{
	pdfauthor={Peter P. Rohde et al.},
	pdftitle={The Quantum Internet -- A New Frontier},
	pdfsubject={Quantum Internet},
	pdfkeywords={Quantum, Computing, Networks, Internet}
}

\makenomenclature
\makeindex
 
\begin{document}

\title{\huge{The Quantum Internet --- A New Frontier}}

\input{Sections/authors}

\date{\today. Version 0.1a}

\frenchspacing

\input{Sections/abstract}

\maketitle

\input{Sections/dedication}

\input{Sections/table_of_contents}

%
% Introduction
%

\part{Introduction}\label{part:introduction}\index{Introduction}

\famousquote{Any sufficiently advanced technology is indistinguishable from magic.}{Arthur C. Clarke}
\newline \newline
\famousquote{There may be babblers, wholly ignorant of mathematics, who dare to condemn my hypothesis, upon the authority of some part of the Bible twisted to suit their purpose. I value them not, and scorn their unfounded judgement.}{Nicolaus Copernicus}\index{Grandad}\index{Mansplaining}
\newline \newline
\famousquote{Imagination is more important than knowledge.}{Albert Einstein}

\if 1\pubmode
\else
	\input{Sections/mission_statement}
\fi

\input{Sections/foreword}
\sketch{sketch_1}

\latinquote{Liber magnus est.}

\input{Sections/introduction}
\sketch{sketch_4}

\latinquote{Vincit qui se vincit.}

%
% Classical networks
%

\part{Classical networks}\label{part:class_net}\index{Classical networks}

\input{Sections/classical_networking_protocols}
\sketch{sketch_7}

\latinquote{Te futueo et caballum tuum.}

\input{Sections/mathematical_representation_of_quantum_networks}
\sketch{sketch_8}

\latinquote{Nil sine magno labore.}

\input{Sections/network_topologies}
\sketch{sketch_21}

\latinquote{Vitam regit fortuna, non sapientia.}

\input{Sections/network_algorithms}
\sketch{sketch_22}

%
% Quantum networks
%

\part{Quantum networks}\label{part:quant_net}\index{Quantum networks}

\input{Sections/quantum_networks}
\sketch{sketch_9}

\latinquote{Gladiator in arena consilium capit.}

\input{Sections/quantum_channels}
\sketch{sketch_10}

\latinquote{Bulla crustulum.}

\input{Sections/optical_encoding_of_quantum_information}
\sketch{sketch_11}

\latinquote{Audaces fortuna juvat.}

\input{Sections/errors_in_quantum_networks}
\sketch{sketch_12}

\latinquote{Igne natura renovatur integra.}

\input{Sections/costs_and_attributes_in_quantum_networks}
\sketch{sketch_13}

\latinquote{Flectere si nequeo superos, acheronta movebo.}

\input{Sections/QTCP}
\sketch{sketch_14}

\latinquote{O derint dum metuant.}

\input{Sections/QTCP_protocol_stack}
\sketch{sketch_37}

\latinquote{Divide et impera.}

\input{Sections/collision_handling_and_classical_errors}
\sketch{sketch_15}

\latinquote{Esse est percipi.}

\input{Sections/multi_packet_operations}
\sketch{sketch_17}

\latinquote{Capax infiniti.}

\input{Sections/extensibility_of_QTCP}
\sketch{sketch_18}

\latinquote{Cedere nescio.}

\input{Sections/scalability_of_QTCP}
\sketch{sketch_41}

\latinquote{Citius altius forties.}

\input{Sections/quality_of_service}
\sketch{sketch_16}

\latinquote{Ex luna scientia.}

\input{Sections/routing_strategies}
\sketch{sketch_19}

\latinquote{Disce quasi semper victurus vive quasi cras moriturus.}

\input{Sections/interconnecting_and_interfacing_quantum_networks}
\sketch{sketch_20}

\latinquote{Vir sapit qui pauca loquitur.}

% Topologies & algorithms were here

\input{Sections/optical_routers}
\sketch{sketch_23}

\latinquote{Semper inops quicumque cupit.}

\input{Sections/optical_stability_in_quantum_networks}
\sketch{sketch_24}

\latinquote{Dum inter homines sumus, colamus humanitatem.}

%
% Protocols for the quantum internet
%

\part{Protocols for the quantum internet}\label{part:protocols}\index{Protocols}

\input{Sections/protocols_for_the_quantum_internet}
\sketch{sketch_26}

\latinquote{Etiam capillus unus habet umbram.}

%
% Entanglement distribution
%

\part{Entanglement distribution}\label{part:ent_dist}
\index{Entanglement!Distribution}

\input{Sections/entanglement_the_ultimate_quantum_resource}
\sketch{sketch_30}

\latinquote{Credo in unum deum.}

\input{Sections/quantum_repeater_networks}
\sketch{sketch_31}

\latinquote{Acta non verba.}

\input{Sections/the_irrelevance_of_latency}

\latinquote{Ceterum censeo carthaginem delendam esse.}

\input{Sections/the_quantum_sneakernet}
\sketch{sketch_38}

\latinquote{Veritas vos liberabit.}

%
% Quantum cryptography
%

\part{Quantum cryptography}\label{part:quant_crypto}\index{Quantum cryptography}

\input{Sections/cryptowars}
\sketch{sketch_39}

\latinquote{A mari usque ad mare.}

%
% Quantum computing
%

\part{Quantum computing}\label{part:QC}\index{Quantum computing}

\input{Sections/models_for_quantum_computation}
\sketch{sketch_5}

\latinquote{Aqua vitae.}

\input{Sections/quantum_algorithms}
\sketch{sketch_25}

\latinquote{Sic semper tyrannis.}

\input{Sections/physical_architectures_for_quantum_computing}
\sketch{sketch_6}

\latinquote{Acta deos numquam mortalia fallunt.}

%
% Cloud quantum computing
%

\part{Cloud quantum computing}\label{part:cloud_QC}\index{Cloud quantum computing}

\input{Sections/cloud_quantum_computing}
\sketch{sketch_27}

\latinquote{Timendi causa est nescire.}

\input{Sections/encrypted_cloud_quantum_computing}
\sketch{sketch_28}

\latinquote{Audentes fortuna iuvat.}

\input{Sections/verification_of_cloud_quantum_computing}
\sketch{sketch_29}

\latinquote{Semper fidelis.}

%
% Economics & Politics
%

\part{Economics \& politics}\label{part:economics}\index{Economics}\index{Politics}

\input{Sections/economics_of_the_quantum_internet}
\sketch{sketch_2}

\clearpage

%
% State of the art
%

\part{History \& state-of-the-art}\label{part:SotA}\index{State-of-the-art}\index{History}

\input{Sections/state_of_the_art}
\sketch{sketch_34}

\clearpage 

%
% To the future & beyond
%

\part{To the future \& beyond}\label{part:future_beyond}

\input{Sections/to_the_future_and_beyond}

\latinquote{Excelsior.}

\input{Sections/the_quantum_space_race}
\sketch{sketch_32}

\latinquote{Volens et potens.}

\input{Sections/quantum_genetic_medicine}
\sketch{sketch_40}

\latinquote{Annus mirabilis.}

\input{Sections/the_quantum_mind}
\sketch{sketch_33}

\latinquote{Grandescunt aucta labore.}

%\input{Sections/quantum_biology}

%\latinquote{Natura nihil frustra facit.}

\input{Sections/optimising_the_world}

\latinquote{Ceteris paribus.}

%
% Essays - A New Frontier
%

\part{Essays -- A new frontier}\label{part:essays}\label{part:essays}\index{Essays}\index{A new frontier}

\input{Sections/a_new_frontier_towards_the_singularity}
\sketch{sketch_35}

%
% The end
%

\part{The end}\label{part:the_end}

\input{Sections/conclusion_the_vision_of_the_quantum_internet}
\sketch{sketch_3}

\famousquote{We will either go down as the world's greatest statesmen, or its greatest villains}{Hermann G{\" o}ring}

\input{Sections/how_to_learn_more}

\if 1\pubmode
\else
	\input{Sections/epilogue}
	\sketch{sketch_36}
\fi

\latinquote{Opus dei.}

\input{Sections/acknowledgements}
\sketch{sketch_2}

\latinquote{Dum spiro, spero.}

\input{Sections/statement_of_contributions}

\input{Sections/list_of_abbreviations}

\bibliography{quantum_internet}

\input{Sections/index}

\input{Sections/about_the_authors}

\sketch{sketch_final}

\end{document}