% The Quantum Internet - A New Frontier
% Peter P. Rohde et al.

\def\pubmode{2}

% Publication mode:
%   0 = Draft without figures
%   1 = Dowling's eyes only
%   2 = Serious draft
%   3 = Arxiv (not serious, 2 column)
%	4 = Publisher (book)

\input{Sections/publication_mode}
\input{Sections/packages}
\input{Sections/commands_and_definitions}

\hypersetup{
	pdfauthor = {Peter P. Rohde},
	pdftitle = {The Quantum Internet},
	pdfsubject = {Quantum Internet},
	pdfkeywords = {Quantum, Computing, Information, Networks, Internet, Cryptography}
}

\makenomenclature
\makeindex

\begin{document}

%
% Entanglement distribution
%

\part{Entanglement distribution}\label{part:ent_dist}\index{Entanglement!Distribution}

\input{Sections/entanglement_the_ultimate_quantum_resource}

\latinquote{Credo in unum deum.}

\input{Sections/quantum_repeater_networks}

\latinquote{Acta non verba.}

\input{Sections/the_irrelevance_of_latency}

\latinquote{Ceterum censeo carthaginem delendam esse.}

%\input{Sections/the_quantum_sneakernet}

\latinquote{Veritas vos liberabit.}

\sketch{sketch_7}

%
% Quantum cryptography
%

\part{Quantum cryptography}\label{part:quant_crypto}\index{Quantum cryptography}

\input{Sections/cryptowars}

\latinquote{A mari usque ad mare.}

\sketch{sketch_8}

%
% Quantum computing
%

\part{Quantum computing}\label{part:QC}\index{Quantum computing}

\input{Sections/models_for_quantum_computation}

\latinquote{Aqua vitae.}

\input{Sections/quantum_algorithms}

\latinquote{Sic semper tyrannis.}

\input{Sections/physical_architectures_for_quantum_computing}

\latinquote{Acta deos numquam mortalia fallunt.}

\sketch{sketch_9}

%
% Cloud quantum computing
%

\part{Cloud quantum computing}\label{part:cloud_QC}\index{Cloud quantum computing}

\input{Sections/cloud_quantum_computing}

\latinquote{Timendi causa est nescire.}

%\input{Sections/encrypted_cloud_quantum_computing}

\latinquote{Audentes fortuna iuvat.}

%\input{Sections/verification_of_cloud_quantum_computing}

\latinquote{Semper fidelis.}

\sketch{sketch_10}

\bibliography{quantum_internet, nana_ML}

\end{document}
